\LARGE \bf Cascading Situation Assessment for Robots

### 2017-02-27 paper.tex
Proof read part 3

As mentioned at section~\ref{arch}, \uwds uses Google's gRPC as message passing
protocol. The protocol is explicitly defined (using the \emph{protocol
buffers}\footnote{\url{https://developers.google.com/protocol-buffers/}}
interface definition language), and bindings to various languages
and platforms can be automatically generated from the protocol definition file
(as of Feb 2017, gRPC can generate bindings for C, C++, C\#, Node.js, PHP, Ruby,
Python, Go and Java on Windows, Mac and Linux).

The cross-platform/cross-language support of gRPC is especially welcomed in the
academic context, as it offers ease and flexibility to plug a variety of
pre-existing components into an \uwds network.

However, the gRPC message passing layer is low-level with respect to the typical
use of \uwds (manipulation of asynchronous, distributed spatio-temporal models
of the robot environment). In particular, the asynchronous fetching (and
conversely, remote updating) of nodes and time-related objects should be
entirely hidden from the user, and managed instead by the \uwds client library.

\uwds currently offers such a high-level client library for Python only. A C++
library is being developed (currently in 'alpha' state).
Listing~\ref{lst|pythonapi} gives a complete example of an \uwds client
performing simple filtering: the client continuously ``listen'' for changes in
an input world, hide some items (in this case, items whose name contain the
string ``{\tt wall}''), and forward all other changes to an output world,
effectively making the output world a copy of the input world with all walls
removed.

@@

with underworlds.Context("walls_filter") as ctx:

@@

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python, and named {\tt
    walls\_filter}: the client connects to the \uwds network, walk through the
    scene graph of world {\tt example\_in}, filter out some objects, and publish
    the remaining objects in the world {\tt example\_out}.}

@@

@@

Interestingly, while \uwds deals with 3D geometries and scenes, it does
represent 3D entities purely as data structures: no visual representation is
involved (and as such, the \uwds server and core libraries do not depend on any
graphics library like OpenGL). However, for all practical purposes, the ability
to visualize the content of a scene is desirable. \uwds provides a standard
client, {\tt uwds view}, that performs real-time 3D rendering of the scene,
using OpenGL (Figure~\ref{fig|uwds-view}).

This tool also support basic object manipulations, that are broadcasted to the
other \uwds clients as expected.

@@

Geometric data like meshes can be loaded into a world (or rather, into the whole
network as geometric data are treated as immutable resources shared amongst all
worlds) by simply sending an array of vertices and faces to the \uwds server.
As such, any client can load 3D data that is automatically made available to the
whole network. For example, an object recognition module recognizes a new
object. It sends the mesh to the \uwds server and creates a new node which
references the mesh. At the next frame update, the 3D viewer sees a new node
referencing a yet unknown mesh. The viewer request the mesh data from the
server, stores it internally (\eg as an OpenGL buffer), and renders it. Whenever
the node transformation is updated, the 3D viewer can re-render it without
having to download the mesh from the server again.

Often, objects manipulated by the robot have known meshes with corresponding CAD
models. In these case, \uwds provides a tool, {\tt uwds load}, that loads a mesh
into a \uwds network (and optionally, creates a node) from a large range of 3D
format\footnote{The underlying import capability is provided by the {\sc assimp}
library.  \url{http://assimp.sourceforge.net/}} (including Collada, FBX, OBJ,
Blender).

@@

\uwds provides a range of tools to inspect a running the network. Graphical
tools ({\tt uwds explorer} and {\tt uwds timeline}, see Figure~\ref{fig|explorer})
provide an user-friendly overview of the system's graph with the connections
between the clients and the worlds as well as their activity.

@@

The {\tt uwds tf} root client continuously monitor the ROS TF tree, and mirror
TF frames as nodes in a given \uwds world. A node is first created if none
matches a given TF frame, and its transformation is subsequently updated,
mirroring the TF frame. A regular expression can be provided to only mirror a
subset of the TF tree into \uwds.

@@

\uwds also implement an efficient algorithm to assess object visibility from a
specific viewpoint (\ie from a given \emph{camera} node). The algorithm (color
picking) enables fast (single pass) computation of the visibility of every
object in the scene, while providing control regarding how much of an object
should be actually visible to be considered as globally visible. The
command-line tool {\tt uwds visibility} returns the list of visible objects from
the point of view of every camera in a given world, and \uwds also provides the
helper class {\tt VisibilityMonitor} to programmatically access visibility
information.

When integrated into a filter node, visibility computation enables to easily
create new worlds representing the estimated perspectives of the different
agents. Listing~\ref{lst|humanperspective} provides the complete code of such an
\uwds client.

>>>>

As mentioned, \uwds uses Google's gRPC as message passing protocol. The protocol
is explicitly defined (using the \emph{protocol
buffers}\footnote{\url{https://developers.google.com/protocol-buffers/}}
interface definition language), and bindings to various languages and platforms
can be automatically generated from the protocol definition file (as of Feb
2017, gRPC can generate bindings for C, C++, C\#, Node.js, PHP, Ruby, Python, Go
and Java on Windows, Mac and Linux).  The cross-platform/cross-language support
of gRPC is especially welcomed in the academic context, as it offers ease and
flexibility to plug a variety of pre-existing components into an \uwds network.

However, the gRPC message passing layer is low-level with respect to the typical
use of \uwds (manipulation of asynchronous, distributed spatio-temporal models
of the robot environment). In particular, the asynchronous fetching (and
conversely, remote updating) of nodes and time-related objects is typically
hidden from the user, and managed instead by the \uwds client library.

\uwds currently offers such a high-level client library for Python only (a C++
library is under development).  Listing~\ref{lst|pythonapi} gives a complete
example of an \uwds client performing simple filtering: the client continuously
listen for changes in an input world, removes some objects (in this case, items
whose name contain the string ``{\tt wall}''), and forward all other changes to
an output world, effectively making the output world a copy of the input world
with all walls removed.

@@

# by default, connect to the server on localhost
with underworlds.Context("walls_filter") as ctx:

@@

\end{pythoncode}
    \caption{Example of a simple yet complete \uwds filter, written in Python:
    the client connects to the \uwds network, walk through the scene graph of
    world {\tt example\_in}, filter out some objects, and publishes the
    remaining objects in the world {\tt example\_out}.}

@@

The \uwds package provides several standard clients to perform common tasks on
\uwds networks.

@@

Interestingly, while \uwds deals with 3D geometries and scenes, it does
represent 3D entities purely as data structures: no visual representation is
involved (and as such, the \uwds server and core libraries do not depend on any
graphics library like OpenGL). However, for all practical purposes, the ability
to visualize the content of a scene is desirable. \uwds provides a standard
client, {\tt uwds view}, that performs real-time 3D rendering of worlds,
using OpenGL (Figure~\ref{fig|uwds-view}).

This tool also support basic object manipulations, that are broadcasted to the
other \uwds clients connected to the same world.

@@

Geometric data like meshes can be loaded into a world (or rather, into the whole
network as geometric data are treated as immutable resources shared amongst all
worlds) by simply sending an array of vertices and faces to the \uwds server.
As such, any client can load 3D data that is automatically made available to the
whole network. For example, an object recognition module recognizes a new
object. It sends the mesh to the \uwds server and creates a new node which
references the mesh. At the next frame update, the 3D viewer sees a new node
referencing a yet unknown mesh. The viewer request the mesh data from the
server, stores it internally (\eg as an OpenGL buffer), and renders it. Whenever
the node transformation is updated, the 3D viewer can re-render the node without
having to download the mesh from the server again.

Often, objects manipulated by the robot have known meshes with corresponding CAD
models that can be conveniently pre-loaded. In these case, \uwds provides a
tool, {\tt uwds load}, that loads a mesh into a \uwds network (and optionally,
creates a node) from a large range of 3D format (including Collada, FBX, OBJ,
Blender)\footnote{The underlying import
capability is provided by the {\sc assimp} library.
\url{http://assimp.sourceforge.net/}}.

@@

\uwds provides a range of tools to inspect a running the network. Graphical
tools ({\tt uwds explorer} and {\tt uwds timeline}, see Figure~\ref{fig|explorer})
provide an user-friendly overview of the system's graph with the connections
between the clients and the worlds, as well as their activity.

@@

The {\tt uwds tf} client continuously monitor the ROS TF tree, and mirrors
TF frames as nodes in the desired \uwds world. A node is first created if none
matches a given TF frame, and its transformation is subsequently updated,
mirroring the TF frame. A regular expression can be provided to only mirror a
subset of the TF tree into \uwds.

@@

\uwds also implements an efficient algorithm to assess object visibility from a
specific viewpoint (\ie from a given \emph{perspective} node). The algorithm (color
picking) enables fast (single pass) computation of the visibility of every
object in the scene, while providing control regarding how many pixels should be
actually visible for the object to be considered globally visible. The
command-line tool {\tt uwds visibility} returns the list of visible objects from
the point of view of each camera in a given world, and \uwds also provides the
helper class {\tt VisibilityMonitor} to programmatically access visibility
information.

When integrated into a filter node, visibility computation allows to easily
create new worlds representing the estimated perspectives of the different
agents. Listing~\ref{lst|humanperspective} provides the complete code of such an
\uwds client.
